### 2019-05-29 2-Chapters/2-Chapter/chapter2.tex
Typos

% First chapter begins here
\chapter{Stochastic Multi-Armed Bandits Models}
\label{chapter:2}
\minitoc
% Write miniTOC just after the title
\graphicspath{{2-Chapters/2-Chapter/Images/}}

\newpage
% \TODOL{L'abstract ici est trop long, mais je l'ai écrit avant de commencer le chapitre, pour avoir une idée de ce que je devais faire ! Je couperai à la fin !}

@@

\begin{defn}\label{def:2:uniformlyEfficientAlgorithm}
    An algorithm $\cA$ is \emph{uniformly efficient} if its (mean) regret satisfies
    \begin{equation}
        R_T^{\cA}(I) = \bigO{C_{I,\alpha} T^{\alpha}}
    \end{equation}
    for any value $\alpha>0$ and any problem instance $I\in \cI$,
    where this notation means that the ``constant'' $C_{I,\alpha}$ can depend on the problem instance $I$ and on $\alpha$, but not on the time horizon $T$.
\end{defn}

@@

Similarly to what is considered for the first lower-bound,
a natural question is to know if there is an algorithm that achieve a regret upper-bound of the form $R_T^{\cA}(I) \leq \bigO{\sqrt{K T}}$ for any instance, independently on the problem difficulty.
It is the case for the Exp3 algorithm from \cite{Auer02}, for example.
Since a few years, some algorithms were shown to achieve both a problem-dependent logarithmic and a minimax upper-bounds,
like MOSS in \cite{Audibert2009minimax} or recently \KLUCBpp{} in \cite{Menard17}.

@@

Using the same analysis, if a lower-bound $d$ on the positive gaps is known beforehand, one can find a tuning of $T_0$ that gives a logarithmic regret.
%
Like for the lower-bound, we have $R_T \leq (\max_{k: \Delta_k > 0} \Delta_k) T_0 + p (T - T_0)$, thus $R_T \leq K T_0 + K \exp(-T_0 d^2/4) T$ using Hoeffding's inequality again. Optimizing on $T_0$ gives $T_0 = 4/d^2 \log(d^2 T / 4)$
and proves that the ``explore-then-exploit'' strategy can also obtain an order-optimal regret, $R_T \leq K 4/d^2 (1 + \log(d^2 T / 4)) = \bigO{\log(T)}$, if it is tuned with a fixed time $T_0$ using prior knowledge on the problem (\ie, $d$) and the horizon $T$.
%
This strategy can also achieve $R_T = \bigO{T^{2/3} (K \log(T))^{1/3}}$ without prior knowledge on the problem, as shown in Section~1 of \cite{Slivkins2019}.

@@

For both cases, the strategy obtains a linear regret if it is tuned independently of the problem at hand, but they can be tuned to be efficient (\ie, with logarithmic regret) if lower-bound on the gaps $\Delta_k$ is known.
%  \ie, they require a prior knowledge on the problem difficulty.
As such, they are not applicable on an unknown problem and are less interesting from a practical point-of-view.

>>>>

% First chapter begins here
\chapter{Stochastic Multi-Armed Bandits Models}
\label{chapter:2}

\TODOL{Abstract ici et plus court, et petite introduction !}

\minitoc
% Write miniTOC just after the title
\graphicspath{{2-Chapters/2-Chapter/Images/}}

\newpage

% \TODOL{L'abstract ici est trop long, mais je l'ai écrit avant de commencer le chapitre, pour avoir une idée de ce que je devais faire ! Je couperai à la fin !}

@@

\begin{defn}\label{def:2:uniformlyEfficientAlgorithm}
    An algorithm $\cA$ is \emph{uniformly efficient} if its (mean) regret satisfies
    \begin{equation}
        R_T^{\cA}(I) = \smallO{C_{I,\alpha} T^{\alpha}}
    \end{equation}
    for any value $\alpha>0$ and any problem instance $I\in \cI$,
    where this notation means that the ``constant'' $C_{I,\alpha}$ can depend on the problem instance $I$ and on $\alpha$, but \emph{not} on the time horizon $T$.
\end{defn}

@@

Similarly to what is considered for the first lower-bound,
a natural question is to know if there is an algorithm that achieve a regret upper-bound of the form $R_T^{\cA}(I) \leq \bigO{\sqrt{K T}}$ for any instance, independently on the problem difficulty.
It is the case for the Exp3 algorithm from \cite{Auer02}, for example.
Since a few years, some algorithms were shown to achieve both a problem-dependent logarithmic and a minimax upper-bounds,
like MOSS in \cite{Audibert2009minimax} or recently \KLUCBpp{} in \cite{Menard17},
and such results are usually referred to as ``best of both worlds''.

@@

Using the same analysis, if a lower-bound $d$ on the positive gaps is known beforehand, one can find a tuning of $T_0$ that gives a logarithmic regret.
%
Like for the lower-bound, we have $R_T \leq (\max_{k: \Delta_k > 0} \Delta_k) T_0 + p (T - T_0)$, thus Hoeffding's inequality gives $R_T \leq K T_0 + K \exp(-T_0 d^2/4) T$. Optimizing on $T_0$ gives $T_0 = 4/d^2 \log(d^2 T / 4)$
and proves that the ``explore-then-exploit'' strategy can also obtain an order-optimal regret, $R_T \leq K 4/d^2 (1 + \log(d^2 T / 4)) = \bigO{\log(T)}$, if it is tuned with a fixed time $T_0$ using prior knowledge on the problem (\ie, $d$) and the horizon $T$.
%
This strategy can also achieve $R_T = \bigO{T^{2/3} (K \log(T))^{1/3}}$ without prior knowledge on the problem, as shown in Section~1 of \cite{Slivkins2019}.

@@

For both cases, the strategy obtains sub-optimal regret if it is tuned independently of the problem at hand, but they can be tuned to be efficient (\ie, with logarithmic regret) if a lower-bound on the gaps $\Delta_k$ is known.
%  \ie, they require a prior knowledge on the problem difficulty.
As such, this weakness make them unapplicable on an unknown problem, and so these first strategies are less interesting from a practical point-of-view.

### 2019-05-29 2-Chapters/4-Chapter/CrownCom_17.git/IoT_slotted.tex
Typos

\paragraph{MAB model}
%
We consider the network from the point of view of one dynamic device.
Following a Bernoulli emission process, every times a dynamic device has to communicate with the gateway,
it has to choose one channel (at each transmission $t \geq 1, t \in \mathbb{N}$), denoted as $C(t) = k \in[K]$.
Then, the dynamic device waits in this channel $C(t)$ for an acknowledgement sent by the gateway, during a certain period (\eg, $5$ seconds for the example considered above).
Before sending another message (\ie, at time $t+1$), the dynamic device knows if it received or not this \Ack{} message.
%
For this reason, selecting channel (or arm) $k$ at time $t$ yields a (random) feedback, called a (binary) \emph{reward}, $r_k(t) \in \{0,1\}$, being $0$ if no \Ack{} was received before the next message, or $1$ if \Ack{} was successfully received.
The goal of the dynamic device is to minimize its packet loss ratio, or equivalently, to maximize its number of successful transmissions, or its cumulative reward,
$r_{1 \dots T} := \sum_{t = 1}^T r_{C(t)}(t),$
which is a usual objective in MAB problems.

>>>>

\paragraph{MAB model}
%
We consider the network from the point of view of one dynamic device.
Following a Bernoulli emission process, every times a dynamic device has to communicate with the gateway,
it has to choose one channel (at each transmission $t \geq 1, t \in \mathbb{N}$), denoted as $A(t) = k \in[K]$.
Then, the dynamic device waits in this channel $A(t)$ for an acknowledgement sent by the gateway, during a certain period (\eg, $5$ seconds for the example considered above).
Before sending another message (\ie, at time $t+1$), the dynamic device knows if it received or not this \Ack{} message.
%
For this reason, selecting channel (or arm) $k$ at time $t$ yields a (random) feedback, called a (binary) \emph{reward}, $r_k(t) \in \{0,1\}$, being $0$ if no \Ack{} was received before the next message, or $1$ if \Ack{} was successfully received.
The goal of the dynamic device is to minimize its packet loss ratio, or equivalently, to maximize its number of successful transmissions, or its cumulative reward,
$r_{1 \dots T} := \sum_{t = 1}^T r_{A(t)}(t),$
which is a usual objective in MAB problems.
